API design for machine learning software: experiences from the scikit-learn project

### 2013-06-28 paper.tex
missing comma spotted by @vene

In \sklearn, model selection is supported in two distinct meta-estimators,
\texttt{GridSearchCV} and \texttt{RandomizedSearchCV}.  They take as input an
estimator (basic or composite), whose hyper-parameters must be optimized, and a
set of hyperparameter settings to search through.
This set is represented as a mapping of parameter names
to a set of discrete choices in the case of grid search,
which exhaustively enumerates the ``grid'' (cartesian product)
of complete parameter combinations.
Randomized search is a smarter algorithm
that avoids the combinatorial explosion in grid search
by sampling a fixed number of times from its parameter distributions
(see \citealt{bergstra2012}).

>>>>

In \sklearn, model selection is supported in two distinct meta-estimators,
\texttt{GridSearchCV} and \texttt{RandomizedSearchCV}.  They take as input an
estimator (basic or composite), whose hyper-parameters must be optimized, and a
set of hyperparameter settings to search through.
This set is represented as a mapping of parameter names
to a set of discrete choices in the case of grid search,
which exhaustively enumerates the ``grid'' (cartesian product)
of complete parameter combinations.
Randomized search is a smarter algorithm
that avoids the combinatorial explosion in grid search
by sampling a fixed number of times from its parameter distributions
(see \citealp{bergstra2012}).
